---
title: "HW07"
author: "107070008"
output: pdf_document
---
# Question 1)  Let’s develop some intuition about the data and results:

## (a)What are the means of viewers’ intentions to share (INTEND.0) on each of the four media types?

```{r 1a}
data1 <- read.csv("./pls-media/pls-media1.csv")
data2 <- read.csv("./pls-media/pls-media2.csv")
data3 <- read.csv("./pls-media/pls-media3.csv")
data4 <- read.csv("./pls-media/pls-media4.csv")

max.len <- max(length(data1$INTEND.0), length(data2$INTEND.0), 
               length(data3$INTEND.0), length(data4$INTEND.0))
datas <- data.frame(
  d1 = c(data1$INTEND.0, rep(NA, max.len - length(data1$INTEND.0))),
  d2 = c(data2$INTEND.0, rep(NA, max.len - length(data2$INTEND.0))),
  d3 = c(data3$INTEND.0, rep(NA, max.len - length(data3$INTEND.0))),
  d4 = c(data4$INTEND.0, rep(NA, max.len - length(data4$INTEND.0)))
)
means <- sapply(datas, mean, na.rm=TRUE)
means
```

## (b)Visualize the distribution and mean of intention to share, across all four media. (Your choice of data visualization; Try to put them all on the same plot and make it look sensible)

```{r 1b}
boxplot(data1$INTEND.0, data2$INTEND.0, data3$INTEND.0, data4$INTEND.0, 
        horizontal = TRUE, col = "skyblue", main = "distribution and mean of intention")
mean1 <- mean(data1$INTEND.0)
mean2 <- mean(data2$INTEND.0)
mean3 <- mean(data3$INTEND.0)
mean4 <- mean(data4$INTEND.0)
abline(v = mean1, col = "red", lwd = 2)
abline(v = mean2, col = "green", lwd = 2)
abline(v = mean3, col = "yellow", lwd = 2)
abline(v = mean4, col = "pink", lwd = 2)
```

## (c) From the visualization alone, do you feel that media type makes a difference on intention to share?
  `Yes, people prefer to share text with each other, and they are a little bit less inclined to share pictures and audio.`

# Question 2) Let’s try traditional one-way ANOVA:

## (a) State the null and alternative hypotheses when comparing INTEND.0 across four groups in ANOVA 
   $H_{null} : \mu_{1}=\mu_{2}=\mu_{3}=\mu_{4}$
   
   $H_{alt} : \mu_{1}\neq\mu_{2} ;\mu_{1}\neq\mu_{3} ;\mu_{1}\neq\mu_{4} ;\mu_{2}\neq\mu_{3} ;\mu_{2}\neq\mu_{4} ;\mu_{3}\neq\mu_{4}$
         
## (b) Let’s compute the F-statistic ourselves:
##    i.  Show the code and results of computing MSTR, MSE, and F
##    ii. Compute the p-value of F, from the null F-distribution; is the F-value significant?
##        If so, state your conclusion for the hypotheses.
```{r 2b}
means <- c(mean1, mean2, mean3, mean4)
sstr <- (length(data1$INTEND.0)*((mean1 - mean(means))^2)+length(data2$INTEND.0)
         *((mean2 - mean(means))^2)+length(data3$INTEND.0)*((mean3 - mean(means))^2)
         + length(data4$INTEND.0)*((mean4 - mean(means))^2))
df_mstr <- 4 - 1
mstr <- sstr/df_mstr
mstr
var1 <- sd(data1$INTEND.0)^2
var2 <- sd(data2$INTEND.0)^2
var3 <- sd(data3$INTEND.0)^2
var4 <- sd(data4$INTEND.0)^2
vars <- c(unname(sapply(datas, var, na.rm=TRUE)))
sse<- (length(data1$INTEND.0)-1)*vars[1]+(length(data2$INTEND.0)-1)*vars[2]+
  (length(data3$INTEND.0)-1)*vars[3]+(length(data4$INTEND.0)-1)*vars[4]
df_mse <- length(data1$INTEND.0) + length(data2$INTEND.0) + length(data3$INTEND.0) + 
  length(data4$INTEND.0)- 4
mse <- sse/df_mse
mse
f_value <- mstr/mse
f_value
p_value <- pf(f_value, df_mstr, df_mse, lower.tail=FALSE)
p_value
```

`f-value > p-value in lower tail, so we should reject our null hypothesis.`

## (c) Conduct the same one-way ANOVA using the aov() function in R – confirm that you got similar results.

```{r 2c}
library(reshape2)
test <- melt(datas, na.rm = TRUE, id.vars = NULL, variable.name = "media",
             value.name = "intend")
oneway.test(test$intend~factor(test$media), var.equal=TRUE)
summary(aov(test$intend~factor(test$media)))
```

## (d) Regardless of your conclusions, conduct a post-hoc Tukey test (feel free to use the TukeyHSD() function in R) to see if any pairs of media have significantly different means – what do you find?

```{r 2d}
anova_model <- aov(test$intend~factor(test$media))
TukeyHSD(anova_model, conf.level= 0.01)
```
`There is no significant different in those groups.`

## (e) Do you feel the classic requirements of one-way ANOVA were met?
## (Feel free to use any combination of methods we saw in class or any analysis we haven’t covered)
`Not Really. Some of the groups are not normall distribution, so we need to use Kruskal Wallis test.`

# Question 3) Let’s use the non-parametric Kruskal Wallis test:

## (a) State the null and alternative hypotheses (in terms of distribution or difference of mean ranks) 
   $H_{null} : \mu_{1}=\mu_{2}=\mu_{3}=\mu_{4}$
   
   $H_{alt} : \mu_{1}\neq\mu_{2} ;\mu_{1}\neq\mu_{3} ;\mu_{1}\neq\mu_{4} ;\mu_{2}\neq\mu_{3} ;\mu_{2}\neq\mu_{4} ;\mu_{3}\neq\mu_{4}$
   
## (b) Let’s compute (an approximate) Kruskal Wallis H ourselves:
##    i.  Show the code and results of computing H:
##    ii. Compute the p-value of H, from the null chi-square distribution; is the H value significant? If so, state your conclusion of the hypotheses.

```{r 3b}
sales_ranks <- rank(test$intend, na.last = NA)

group_ranks <- split(sales_ranks, test$media)

group_ranksums <- sapply(group_ranks, sum) #, na.rm=TRUE)))

group_length <- sapply(group_ranks, length)

N <- length(test$intend)
H <- (12/N*(N+1))*sum((group_ranksums^2)/group_length)-3*(N+1)
H
kw_p <- 1 - pchisq(H, df=4-1)
kw_p
```

## (c) Conduct the same test using the kruskal.wallis() function in R – confirm that you got similar results.

```{r 3c}
kruskal.test(intend ~ media, data = test)
```

`kw_p = 0, p-value of kruskal-Wallis rank sum test is 0.03166. They are similar.`

## (d) Regardless of your conclusions, conduct a post-hoc Dunn test (feel free to use the dunnTest() function from the FSA package) to see if any pairs of media are significantly different – what do you find?

```{r 3d}
library(FSA)
dunnTest(intend ~ media, data = test, method = "bonferroni")
```

`d1-d4 is significant different. Its P.adj is less than 0.05, and its abs(z value) is the greatest one among other datas.`
