---
title: "HW15"
author: "107070008"
output: pdf_document
always_allow_html: true
---

```{r hw15}
library(seminr)
sec = read.csv("security_data_sem.csv")
```

# Question 1) Composite Path Models using PLS-PM

## a. Create a PLS path model using SEMinR, with all the following characteristics:
### i. Measurement model - all constructs are measured as composites:**
* **1.Trust in website (TRUST): items TRST1 - TRST4**
* **2.Perceived security of website (SEC): items PSEC1 - PSEC4**
* **3.Reputation of website (REP): items PREP1 - PREP4**
* **4.Investment in website (INV): items PINV1 - PINV3**
* **5.Perception of privacy policies (POL): items PPSS1 - PPSS3**
* **6.Familiarity with website (FAML): item FAML1 (see the documentation of SEMinR for making single item constructs)**
* **7.Interaction between REP and POL (use orthogonalized product terms)**

```{r Q1ai}
#Measurement Model
sec_mm <- constructs(
  composite("TRUST", multi_items("TRST", 1:4)),
  composite("SEC", multi_items("PSEC", 1:4)),
  composite("REP", multi_items("PREP", 1:4)),
  composite("INV", multi_items("PINV", 1:3)),
  composite("POL", multi_items("PPSS", 1:3)),
  composite("FAML", multi_items("FAML", 1:1)),
  interaction_term(iv ="REP", moderator ="POL", method = orthogonal)
)
```
### ii. Structural Model - paths between constructs as shown in this causal model: REP+INV+ POL+FAML+(REP*POL)-> SEC -> TRUST
```{r Q1aii}
#Structural Model
sec_sm <- relationships(
  paths(from = c("REP", "INV", "POL", "FAML", "REP*POL"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
)
```
## b.Show us the following results in table or figure formats:
* **i.Plot a figure of the estimated model**
```{r Q1bi}
sec_pls <- estimate_pls(data = sec, 
                        measurement_model = sec_mm, 
                        structural_model = sec_sm)
plot(sec_pls)
```

* **ii.Weights and loadings of composites**
```{r Q1bii}
sec_report <- summary(sec_pls)
sec_report$weights
head(sec_report$loadings)
tail(sec_report$loadings)
```

* **iii.Regression coefficients of paths between factors**
```{r Q1biii}
sec_report$path
```

* **iv.*Bootstrapped path coefficients: t-values, 95% CI**
```{r Q1biv}
boot_pls <- bootstrap_model(sec_pls, nboot= 1000, cores = 4, seed = NULL)
boot_pls_report <- summary(boot_pls)
CI_2.5 <- boot_pls_report$bootstrapped_paths[, "2.5% CI"]
CI_97.5 <-  boot_pls_report$bootstrapped_paths[, "97.5% CI"]
tvalues <- boot_pls_report$bootstrapped_paths[, "T Stat."]
data.frame(tvalues, CI_2.5, CI_97.5)
```

# Question 2) Common-Factor Models using CB-SEM

## a. Create a common factor model using SEMinR, with the following characteristics:
### i. Either respecify all the constructs as being reflective(), or use the as.reflective()
```{r Q2ai}
sec_cf_mm <- as.reflective(sec_mm)
```
 
### ii. function to convert your earlier measurement model to being entirely reflective.
Use the same structural model as before (you can just reuse it again!)**
```{r Q2aii}
sec_cf_sm <- sec_sm
```
 

## b. Show us the following results in table or figure formats
### i. Plot a figure of the estimated model (it will look different from your PLS model)
```{r Q2bi}
sec_cf_pls <- estimate_cbsem(data = sec, 
                        measurement_model = sec_cf_mm, 
                        structural_model = sec_cf_sm)
library(semPlot)
plot(sec_cf_pls)
```
 
### ii. Loadings of composites
```{r Q2bii}
sec_cf_report <- summary(sec_cf_pls)
sec_cf_report$loadings
```
 
### iii. Regression coefficients of paths between factors, and their pvalues
```{r Q2biii}
sec_cf_report$paths$coefficients
sec_cf_report$paths$pvalues
```
 
