---
title: "HW01"
author: '107070008'
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

1.What is the 5th element in the original list of ages?

```{r first}
my_data <- read.csv("./customers.csv")
my_data[5,]
```

2.What is the fifth lowest age?
```{r second}
fifth_lowest<-sort(my_data$age, FALSE)[5]
fifth_lowest
```

3.Extract the five lowest ages together.
```{r 3}
five<-sort(my_data$age, FALSE)[1:5]
five
```

4.Get the five highest ages by first sorting them in decreasing order first.
```{r 4}
sort_data <- sort(my_data$age, decreasing = TRUE)
sort_data[1:5]
```

5.What is the average (mean) age?
```{r 5}
mean(sort_data)
```

6.What is the standard deviation of ages?
```{r 6}
sd(sort_data)
```

7."age_diff" = the difference between each age and the mean age.
```{r 7}
age_diff <- my_data$age-mean(my_data$age)
age_diff
```

8.What is the average “difference between each age and the mean age”?
```{r 8}
mean(age_diff)
```

9.Visualize the raw data: (a) histogram, (b) density plot, (c) boxplot+stripchart
```{r 9}
#(a) histogram
hist(my_data$age, main="histogram", xlab="numbers", ylab="ages") 
#(b) density plot
plot(density(my_data$age), main = "Density Plot", xlab = "ages", ylab = "density")
#(c) boxplot+stripchart
boxplot(my_data$age, main = "boxplot + stripchart", xlab = "ages", horizontal = TRUE)
stripchart(my_data$age, add = TRUE, method = "stack")
```

